Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems

### 2019-05-07 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated text

\title{Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems\\
% \thanks{Identify applicable funding agency here. If none, delete this.}
}
%
%\author{\IEEEauthorblockN{Alessandro Trindade}
%\IEEEauthorblockA{
%\textit{Federal University of Amazonas}, Brazil \\
%alessandrotrindade@ufam.edu.br}
%\and
%\IEEEauthorblockN{Lucas Cordeiro}
%\IEEEauthorblockA{
%\textit{University of Manchester}, UK \\
%lucas.cordeiro@manchester.ac.uk }
%}
%
\maketitle

\begin{abstract}
Currently, there exist various state-of-the-art tools to design solar photovoltaic (PV) systems, but they are mainly based on simulations, which do not cover all aspects of the design-space. We present a sound and automated approach to synthesize optimal sizing of stand-alone PV systems using program synthesis. 
In particular, our counterexample guided inductive synthesis (CEGIS) approach has two phases: we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost. The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained. Commercial equipment data is provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of two different intricate case studies.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Cyber-Physical Systems  (CPS) are engineered systems, which are built from, and depend upon, 
the seamless integration of computational  and  physical  components~\cite{NSF2015}. 
During operation, such components must frequently adapt to the executing environment changes 
faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].
%Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, 
%unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
%
%While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}. 
Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS. Those techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS. In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}. Energy production, distribution, and optimization are all CPS problems~\cite{UC}.

@@

In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 However, those tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}. 
 Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed~\cite{Alsadi2018}.

However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, which can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}. Here, we use counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as starting point and then incrementally produce a sequence of candidate solutions that satisfy $\sigma$. In particular, we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost. The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained from financial analysis.

Our work makes two major contributions. Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
%
%-----------------------------------------------------------
\section{BACKGROUND}
\label{sec:AutomatedVerification}
%-----------------------------------------------------------
%
%-----------------------------------------------------------
\subsection{Program Synthesis}
\label{sec:ProgramSynthesis}
%-----------------------------------------------------------
%
The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$. In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that satisfy $\sigma$~\cite{Abateetal2017}. As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely. CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur13}.

@@

In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs} that is incrementally updated. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify}, in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again. 
%
\begin{figure}[h]
	\centering
	\includegraphics[width=0.85\columnwidth]{fig2_rev.jpg}
	\caption{CEGIS applied to PV system sizing.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}
%
One may notice that each iteration of the CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.  Given that the full set of inputs $\mathcal{D}$ is finite, this means that the refinement loop can only iterate over a finite number of times; however, $\mathcal{D}$ can represent a large number of elements for the finite set $\text{\sc inputs}$ and our synthesis engine can then conclude that no feasible equipment combination was found. 
%In order to avoid exploring all possible values, machine learning techniques can be used in the phase {\sc synthesize}, with the goal of learning from experience (input-output samples), {\it i.e.}, learning from counterexamples provided by a verification oracle~\cite{Alur13}. In addition to that, a pre-processing stage could also figure as another block in the scheme shown in Fig. \ref{Counter-Example-Guided-Inductive-Synthesis}, between {\sc verify} and {\sc synthesize}, which would process counterexamples and provide larger and refined information to the latter, according to specification $\sigma$ and domain $\mathcal{D}$, in order to speed-up convergence to a final candidate.

Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{Sharma14}; here we have used software verifiers based on SMT solvers.%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.

@@

The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into Direct Current (DC) electricity. %In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$). 
For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an Alternating Current (AC) load, a DC/AC conversion is required. That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.

@@

Here the sizing check will be automatically performed by our proposed method; this stage will ensure that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice. 

@@

To select an optimal combination of components from a PV system to meet sizing constraints, 

@@

the ideal solution is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 

@@

Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.

@@

The main challenge for the {\sc Verify} phase is to find a feasible candidate solution regarding the constraints and user requirements, which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our {\sc Synthesize} phase. 
Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------
\textbf{Case studies and setup.} We have performed two stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}. Our synthesis algorithm was fed with data and costs of twenty-two equipment items from nine different manufacturers of PV systems. Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency. 
All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
The experiments were performed with a predefined timeout of $240$ minutes.

@@

\textbf{Results.}  CPAchecker was able to synthesize the optimal sizing of both case studies: the result was produced in $50.2$ and $37.2$ minutes, respectively. 
The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 22 from Algorithm~\ref{alg:verification-algorithm}. The results were tested by manual PV sizing and were sound (\textit{RQ1}). %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code. 
CBMC and ESBMC produced \textit{UNKNOWN} result (\textit{timeout} or \textit{out of memory}); this partially answers the \textit{RQ2}.
%
%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
\begin{table}
\caption{Case studies and Results: optimization of PV systems.}\label{tab1}
%\begin{scriptsize}
\begin{tabular}{|c|c|c|}
\hline
\hline
Specification & \makecell{ \textbf{Case Study 1} \\ Demand=501W \\ Peak=501W \\ Energy=3,900Wh/day\\Battery autonomy=48h\\AC Voltage=120V\\DoD=25\%\\Vsystem=24V DC} & \makecell{\textbf{Case Study 2}\\ Demand=915W \\ Peak=980W \\Energy=4,880Wh/day\\Battery autonomy=6h\\AC Voltage=120V\\DoD=25\%\\Vsystem=24V DC}\\
\hline
\hline
Tools & \textbf{Result} & \textbf{Result}\\
\hline
\makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{UNKNOWN \\(Out of Memory)} & \makecell{UNKNOWN \\(Out of Memory)}\\
\hline
\makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{UNKNOWN \\(Timeout)} & \makecell{UNKNOWN \\(Timeout)} \\
\hline
%UAutomizer 0.1.24 (Z3 4.8.3) & UNKNOWN & UNKNOWN \\
%\hline
\makecell{CPAchecker 1.8\\(MathSAT 5.5.3)} & \makecell{SAT (50.2 min) \\Property violation line 209\\NTP=1$\times$330W (1S)\\NBT=8$\times$105Ahm (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\Total Cost=US\$ 1,902.60} & \makecell {SAT (37.2 min) \\Property violation line 209\\NTP=3$\times$330W (3S)\\NBT=2$\times$105Ah (2S)\\Controller 35A/145V\\Inverter 1,500VA/24V \\Total Cost=US\$ 2,235.57}\\
\hline
\hline
\end{tabular}
%\end{scriptsize}
\end{table}

\textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with a off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
%
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{trindadeThesis_menor}{}
\vspace{12pt}
\end{document}

>>>>

\title{Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems}
%
%\author{\IEEEauthorblockN{Alessandro Trindade}
%\IEEEauthorblockA{
%\textit{Federal University of Amazonas}, Brazil \\
%alessandrotrindade@ufam.edu.br}
%\and
%\IEEEauthorblockN{Lucas Cordeiro}
%\IEEEauthorblockA{
%\textit{University of Manchester}, UK \\
%lucas.cordeiro@manchester.ac.uk }
%}
%
\maketitle

\begin{abstract}
Currently, there exist various state-of-the-art tools to design solar photovoltaic (PV) systems, but they are mainly based on simulations, which do not cover all aspects of the design-space. We present a sound and automated approach to synthesize optimal sizing of stand-alone PV systems using program synthesis. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost. The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained. Commercial equipment data is provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of two different intricate case studies.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Cyber-Physical Systems  (CPS) are engineered systems, which are built from, and depend upon, 
the seamless integration of computational  and  physical  components~\cite{NSF2015}. 
During operation, such components must frequently adapt to the executing environment changes 
faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].
%Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, 
%unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
%
%While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}. 
Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS. These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS. In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}. Energy production, distribution, and optimization are all CPS problems~\cite{UC}.

@@

In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}. 
 Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed~\cite{Alsadi2018}.

However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, which can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}. Here, we use counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$. In particular, in each iteration, we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost. The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained from financial analysis.

Our work makes two major contributions. Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing PV sizing is unprecedented. Here, a list of PV components %(i.e., PV panels, charge controllers, inverters, and batteries) 
can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
%
%-----------------------------------------------------------
\section{BACKGROUND}
\label{sec:AutomatedVerification}
%-----------------------------------------------------------
%
%-----------------------------------------------------------
\subsection{Program Synthesis}
\label{sec:ProgramSynthesis}
%-----------------------------------------------------------
%
The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$. In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}. As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely. CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur13}.

@@

In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs} that is incrementally updated. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify}, in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again. 
	\includegraphics[width=0.85\columnwidth]{fig2_rev.jpg}
	\caption{CEGIS applied to PV system sizing.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
One may notice that each iteration of the CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.  Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $\text{\sc inputs}$ exists and our synthesis engine can then conclude that no feasible equipment combination was found. At this specific automated formal synthesis of PV systems, we use a variant of CEGIS, where in each iteration we increase the expected cost of PV systems and this controls the {\sc verify} phase and the search by the optimal sizing.  %however, $\mathcal{D}$ can represent a large number of elements for the finite set  and our synthesis engine can then conclude that no feasible equipment combination was found. 
%In order to avoid exploring all possible values, machine learning techniques can be used in the phase {\sc synthesize}, with the goal of learning from experience (input-output samples), {\it i.e.}, learning from counterexamples provided by a verification oracle~\cite{Alur13}. In addition to that, a pre-processing stage could also figure as another block in the scheme shown in Fig. \ref{Counter-Example-Guided-Inductive-Synthesis}, between {\sc verify} and {\sc synthesize}, which would process counterexamples and provide larger and refined information to the latter, according to specification $\sigma$ and domain $\mathcal{D}$, in order to speed-up convergence to a final candidate.
Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications; %, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{Sharma14}; 
here we have used software verifiers based on SMT solvers.%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.

@@

The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. %In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$). 
For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. That converter is called inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.

@@

The sizing check stage will ensure that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice. 

@@

%%%To select an optimal combination of components from a PV system to meet sizing constraints, 

@@

The optimal sizing of PV systems is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 

@@

Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.

@@

The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution regarding the constraints and user requirements. Related to our {\sc Verify} phase the challenge is to find the lowest acquisition cost from a list of equipment and components that is provided from the {\sc Synthesize} phase.

Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------
\textbf{Case studies.} We have performed two stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}. Our synthesis algorithm was fed with data and costs of twenty-two equipment items from nine different manufacturers of PV systems. Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.

\textbf{Setup.} All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
The experiments were performed with a predefined timeout of $240$ minutes.

@@

\textbf{Results.}  CPAchecker was able to synthesize the optimal sizing of both case studies: the result was produced in $50.2$ and $37.2$ minutes, respectively. 
The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 22 from Algorithm~\ref{alg:verification-algorithm}. The results were tested by manual PV sizing and were sound (\textit{RQ1}). %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code. 
CBMC and ESBMC produced \textit{UNKNOWN} result (\textit{timeout} or \textit{out of memory}); this partially answers the \textit{RQ2}.
%
%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
\begin{table}
\caption{Case studies and Results: optimization of PV systems.}\label{tab1}
%\begin{scriptsize}
\begin{tabular}{|c|c|c|}
\hline
\hline
Specification & \makecell{ \textbf{Case Study 1} \\ Demand=501W \\ Peak=501W \\ Energy=3,900Wh/day\\Battery autonomy=48h\\AC Voltage=120V\\DoD=25\%\\Vsystem=24V DC} & \makecell{\textbf{Case Study 2}\\ Demand=915W \\ Peak=980W \\Energy=4,880Wh/day\\Battery autonomy=6h\\AC Voltage=120V\\DoD=25\%\\Vsystem=24V DC}\\
\hline
\hline
Tools & \textbf{Result} & \textbf{Result}\\
\hline
\makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{UNKNOWN \\(Out of Memory)} & \makecell{UNKNOWN \\(Out of Memory)}\\
\hline
\makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{UNKNOWN \\(Timeout)} & \makecell{UNKNOWN \\(Timeout)} \\
\hline
%UAutomizer 0.1.24 (Z3 4.8.3) & UNKNOWN & UNKNOWN \\
%\hline
\makecell{CPAchecker 1.8\\(MathSAT 5.5.3)} & \makecell{SAT (50.2 min) \\Property violation line 209\\NTP=1$\times$330W (1S)\\NBT=8$\times$105Ahm (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\Total Cost=US\$ 1,902.60} & \makecell {SAT (37.2 min) \\Property violation line 209\\NTP=3$\times$330W (3S)\\NBT=2$\times$105Ah (2S)\\Controller 35A/145V\\Inverter 1,500VA/24V \\Total Cost=US\$ 2,235.57}\\
\hline
\hline
\end{tabular}
%\end{scriptsize}
\end{table}
%

\textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
%
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{trindadeThesis_menor}{}
%\vspace{12pt}
\end{document}
